FINE SCALE REGISTRATION OF SIDEWALKS AND OTHER RIBBON-LIKE FEATURES FROM AERIAL IMAGERY

### 2018-07-28 Chapters/5.Conclusion/Conclusion.tex
Adding new figure on intersection

\begin{figure}
    \centering
    \includegraphics[width=0.83\textwidth]{Figures/oxford_fail_1.png}
    \caption[Failure Case 1]{Demonstration on failure cases. Due to the fact that road structures may change overtime. It's possible to produce the output with the input map and the initial trajectory within different time stamp. Sample figure shows our approach produce 'incorrect' sidewalk boundaries because the map data is older than the trajectory so we are producing the sidewalk that were not built yet.}
    \label{fig:oxford_fail_1}
\end{figure}

@@

    \item We'll give hypothesis to process the intersection area. By identify the point that is overlapped as intersection part (same node in multiple ways), we connect nodes on each way that are adjacent to the point. By extend each path a little bit more into the adjacent path to finish the intersection.

@@

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=0.83\textwidth]{Figures/oxford_fail_1.png}
    \caption[Failure Case 1]{Demonstration on failure cases. Due to the fact that road structures may change overtime. It's possible to produce the output with the input map and the initial trajectory within different time stamp. Sample figure shows our approach produce 'incorrect' sidewalk boundaries because the map data is older than the trajectory so we are producing the sidewalk that were not built yet.}
    \label{fig:oxford_fail_1}
\end{figure}

@@

    \item We'll give hypothesis to process the intersection area. We identify the point that is overlapped as intersection part (same node in multiple ways), we connect nodes on each way that are adjacent to the point. By extend each path a little bit more into the adjacent path to finish the intersection. Figure \ref{fig:intersection} shows the basic idea of our hypothesis, the sidewalk from the left merges into the left. It's connecting the left sidewalk into the right one and processed it as the same part.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Figures/intersection.png}
    \caption[Intersection Demonstration]{A hypothesis demonstration on intersection. By extend each path a little bit more into the next adjacent path, we can connect them we a little 'elbow'.}
    \label{fig:intersection}
\end{figure}
